Machine Learning Project Notes

### 2014-05-02 ProjectNotes.tex
fixed typos in tex file

\documentclass{article}

\usepackage{amsmath}
\newcommand{\V}[1]{\boldsymbol{#1}}
\newcommand{\E}[0]{\mathbb{E}}
\title{Machine Learning Project Notes}

@@

Let us let $I_1$ be the set of $t$ where a mistake was made and,
$\hat{y}=1$.  Let $I_2$ be the set where a mistake was made and
$\hat{y} = 0, k = 1$, and let $I_3$ be the set where a mistake was
made, $\hat{y} = 0$ and $k = 0$. Finally, let $M_i = |I_i|$ for $i =
1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
$M$ in the usual perceptron case.  We assume that there exits a $\rho$
and $R$ satisfying the assumptions of theorem 7.8. Let $M' = M_1 + M_2$, then
\begin{align*}
M' =& \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2}
y_t\V{x}_t \\
 \leq & \  \|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t \|\\
= & \ \|\sum_{t \in I_1 \cup I_2} \V{w}_{t+1} - \V{w}_t) \| \\
= & \ \|\V{w}_{T+1} \| \\
= & \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t+1}\|^2 -
  \|\V{w}_t\|^2 }\\
= & \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t} + y_t\V{x}_t\|^2 -
  \|\V{w}_t\|^2 }\\
= & \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t\V{w}_t\cdot \V{x}_t -
  \|\V{x}_t\|^2} \\
\leq & \sqrt{\sum_{t \in I_1 \cup I_2} \|\V{x}_t\|^2} \leq
\sqrt{M'r^2} \\
\Rightarrow M' \leq &\frac{r^2}{\rho^2} \\
\end{align}
We then have that $M = M' + M_3$, so we would like a bound on $M_3$.
Here we revert to a weaker bound, considering the expectation of
$M_3$.  
\begin{align*}
M_3 = & \sum_{I_2} 1_{k = 0} \\
\E[M_3] = & \sum_{I_2} \E[1_{k = 0}] = (1 - p) (M_3 + M_2) \\
M_2 = & \sum_{I_2} 1_{k = 1} \\
\E[M_2] = & p (M_3 + M_2) \\
\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]\\
\end{align}
We may then apply the crude bound $\E[M_3] \leq & \frac{1-p}{p}
M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
\begin{align*}
\E[M]  =  & \E[M'] + \E[M_3] \\
\leq & \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
\leq = \frac{1}{p}\frac{r^2}{\rho^2} \\
\end{align}
Note that this is a weak bound.  Not only is it greater than the
original perceptron bound by a factor of $1/p$, it is also only a
bound in expectation.

>>>>

\documentclass{article}
\usepackage{amssymb}
\usepackage{amsmath}
\newcommand{\V}[1]{\boldsymbol{#1}}
\newcommand{\E}[0]{\mathbb{E}}
\title{Machine Learning Project Notes}

@@

Let us let $I_1$ be the set of $t$ where a mistake was made and,
$\hat{y}=1$.  Let $I_2$ be the set where a mistake was made and
$\hat{y} = 0, k = 1$, and let $I_3$ be the set where a mistake was
made, $\hat{y} = 0$ and $k = 0$. Finally, let $M_i = |I_i|$ for $i =
1,2,3$. We then can bound $M_1 + M_2$ in the same way that we bound
$M$ in the usual perceptron case.  We assume that there exits a $\rho$
and $R$ satisfying the assumptions of theorem 7.8. Let $M' = M_1 + M_2$, then
\begin{align*}
M' =& \frac{\V{v}}{\|\V{v}\|}\sum_{I_1 \cup I_2}
y_t\V{x}_t \\
 \leq & \  \|\sum_{t \in I_1 \cup I_2} y_t \V{x}_t \|\\
= & \ \|\sum_{t \in I_1 \cup I_2} \V{w}_{t+1} - \V{w}_t) \| \\
= & \ \|\V{w}_{T+1} \| \\
= & \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t+1}\|^2 -
  \|\V{w}_t\|^2 }\\
= & \sqrt{\sum_{t \in I_1 \cup I_2} \|  \V{w}_{t} + y_t\V{x}_t\|^2 -
  \|\V{w}_t\|^2 }\\
= & \sqrt{\sum_{t \in I_1 \cup I_2} 2y_t\V{w}_t\cdot \V{x}_t -
  \|\V{x}_t\|^2} \\
\leq & \sqrt{\sum_{t \in I_1 \cup I_2} \|\V{x}_t\|^2} \leq
\sqrt{M'r^2} \\
\Rightarrow M' \leq &\frac{r^2}{\rho^2} \\
\end{align*}
We then have that $M = M' + M_3$, so we would like a bound on $M_3$.
Here we revert to a weaker bound, considering the expectation of
$M_3$.  
\begin{align*}
M_3 = & \sum_{I_2} 1_{k = 0} \\
\E[M_3] = & \sum_{I_2} \E[1_{k = 0}] = (1 - p) (M_3 + M_2) \\
M_2 = & \sum_{I_2} 1_{k = 1} \\
\E[M_2] = & p (M_3 + M_2) \\
\Rightarrow E[M_3] = & \frac{1-p}{p}\E[M_2]
\end{align*}
We may then apply the crude bound $\E[M_3] \leq  \frac{1-p}{p}
M'$, since $M_2 \leq M'$. We then bound the expected number of mistakes with
\begin{align*}
\E[M]  =  & \E[M'] + \E[M_3] \\
\leq & \frac{r^2}{\rho^2} + \frac{1-p}{p}\frac{r^2}{\rho^2} \\
\leq = \frac{1}{p}\frac{r^2}{\rho^2} \\
\end{align*}
Note that this is a weak bound.  Not only is it greater than the
original perceptron bound by a factor of $1/p$, it is also only a
bound in expectation.
